Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-17 cvx-flats-neurips21/cvx-flats.tex
Making neurips21 dir for cvx-flats

\documentclass[anon,12pt]{colt2021} % Anonymized submission
%\documentclass[final]{colt2020} % Anonymized submission
% \renewcommand{\includegraphics}[1][1]{}

% \documentclass{colt2020} % Include author names

@@

\usepackage{times}

\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[small]{caption}
% NOTE: had to comment out "todo" in colt2021.cls
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

@@

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}
%\newtheorem{conjecture}{Conjecture}
%\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{condition}{Condition}
%\newtheorem{remark}{Remark}

@@

% Three or more authors with the same address:
\coltauthor{\Name{Jessie Finocchiaro} \Email{jessica.finocchiaro@colorado.edu}\\
	\Name{Rafael Frongillo} \Email{raf@colorado.edu}\\
	\Name{Bo Waggoner} \Email{bwag@colorado.edu}\\
	\addr CU Boulder}

@@

\begin{figure}[htb]
	\centering
	\begin{tabular}{cc}
		\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} &
		\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
	\end{tabular}
	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) \geq 2$.}
	\label{fig:fsd-flats-abstain}
\end{figure}

@@

This example also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
\begin{figure}
	\centering
	\includegraphics[width=0.3\linewidth]{tikz/t-example.pdf}
	\caption{A meteorology example with a bias towards citizen safety.}
	\label{fig:t-example}
\end{figure}

>>>>

\documentclass{article} % Anonymized submission
% \renewcommand{\includegraphics}[1][1]{}

\usepackage{neurips_2021}

@@

\usepackage{times}
\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts,amsmath,amssymb,amsthm}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

@@

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[small]{caption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{condition}{Condition}
\newtheorem{remark}{Remark}

@@

\author{%
	Jessie Finocchiaro\thanks{Use footnote for providing further information
		about author (webpage, alternative address)---\emph{not} for acknowledging
		funding agencies.} \\
	Department of Computer Science\\
	CU Boulder\\
	\texttt{jefi8453@colorado.edu} \\
	% examples of more authors
	\And
	Raf Frongillo \\
	CU Boulder \\
	\texttt{raf@colorado.edu} \\
	\AND
	Bo Waggoner\\
	CU Boulder \\
	\texttt{bwag@colorado.edu} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

\begin{figure}[htb]
	\centering
	\begin{tabular}{cc}
%		\includegraphics[width=.35\textwidth]{tikz/fsd-bound.pdf} &
%		\includegraphics[width=.35\textwidth]{tikz/flats-bound.pdf} \\
	\end{tabular}
	\caption{(Left) Feasible subspace dimension $\Sc_{\gamma_\bot}(\bullet) = 2$ and $\Sc_{\gamma_\bot}({\color{blue}\star}) = 1$, giving the bound $\conscvx(\ell^{abs}) \geq 3- 1-1 = 1$.
          (Right) No $1$-flat through $\bullet$ (a line since $\bullet \in \relint{\simplex})$  stays fully contained in $\gamma_\bot$, so $\conscvx(\ell^{abs}) \geq 2$.}
	\label{fig:fsd-flats-abstain}
\end{figure}

@@

This example also extends to other decision-tree-like properties that do not have an explicit or easily constructed target loss.
\begin{figure}
	\centering
%	\includegraphics[width=0.3\textwidth]{tikz/t-example.pdf}
	\caption{A meteorology example with a bias towards citizen safety.}
	\label{fig:t-example}
\end{figure}
